---
title: "Most Recent Test Scrape of the VD17"
date: "`r format(Sys.time(), '%B %d, %Y @ %I:%M %p')`"
output: html_document
---

<h3>Note on this page</h3>
This page reports the results of the most recent test of the VD17 scrape, finsished at the date and time noted above.  It is only a test of the scraping program, and only reports 100 random results from 3 random years in the seventeenth century.  Also note that the values for places, languages, etc. come from the raw values supplied by the VD17.  Further processing might change these figures.  

The point of this page is largely to catch any obvious errors as I build the scraping engine.  If you would like to contribute to the program, or examine the code underlying this scrape, vist the [GitHub page](https://github.com/stuckinthe16th/vd17_scrape) for this project.  The full results of the scrape can be downloaded from [here](http://earlymodernprinting.com/data/test_scrape_results.csv).


<h3>Summary Table:</h3>

```{r results='asis', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
scrape_results <- read.csv("http://earlymodernprinting.com/data/test_scrape_results.csv")
scrape_years <- unique(scrape_results$year_gb)
scrape_results_stats <-data.frame()
for(x in 1:length(scrape_years)){
     scrape_results_stats <- rbind(scrape_results_stats, data.frame(year=scrape_years[x], books= nrow(scrape_results[scrape_results$year_gb==scrape_years[x],]), places=length(unique(scrape_results$places_gbv[scrape_results$year_gb==scrape_years[x]])), printers=length(unique(scrape_results$editor_printer_gbv[scrape_results$year_gb==scrape_years[x]])) ,languages=length(unique(scrape_results$languages_gbv[scrape_results$year_gb==scrape_years[x]]))))
     
}
pacman::p_load("hwriter")
library("hwriter")
cat(hwrite(scrape_results_stats, width='50%', center=TRUE, row.bgcolor='#dd3333', row.style=list('font-weight:bold; text-align:center; font-coloer:black')))

```

<h3>Scrape Report</h3>
```{r scrape_report, echo=FALSE}
suppressWarnings(cat(readLines('./test_scrape_output.txt'), sep = '\n'))
```